%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip}


% в преамбулу добавь:

\raggedbottom

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X}

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by:
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{6pt}


%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{0pt}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty}

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Irina Nosal} \\[7.5pt]
\href{https://github.com/Irina-Na}{\raisebox{-0.05\height}\faGithub\ Irina-Na} \ $|$ \
\href{https://linkedin.com/in/irinanosal}{\raisebox{-0.05\height}\faLinkedin\ irinanosal} \ $|$ \
\href{mailto:ironia.i@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ ironia.i@gmail.com} \ $|$ \
\href{tel:+381659438842}{\raisebox{-0.05\height}\faMobile \ +381 65 9438842} \ $|$ \
\end{tabularx}


%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
\section{Summary}
AI tech lead and engineer with Ph.D., expertise in NLP, matching, search, and LLM for business decisions. 15+ years in Tech (Telecom, InfoSec, ML), 8+ years in software dev (Python, SQL, Matlab, C, Assembler), 5+ years commercial. 5+ years in research, 5+ years in AI/ML/DS and 2+ years in AI/ML product management. \href{https://scholar.google.com/citations?user=g1m_ATEAAAAJ&hl=ru}{Has 8+ publications. Hirsh Index 4. }

%Experience 1
\section{Work Experience}

% ---- HAQQ (как AUTODOC/WELLNITE: без tabularx) ----
\noindent\textbf{AI TECH LEAD, AI ENGINEER | \href{https://haqq.network/}{HAQQ Network}}
\hfill \mbox{Mar 2024 -- present}\par
\footnotesize \textbf{Blockchain} ecosystem HAQQ with capital of \$200 million and more then 200 employees.\par

\noindent\textbf{\href{https://www.mmapp.org/}{Expert chatbot for messenger}}
\hfill \textbf{Tech Lead, AI Engineer}\par
\begin{itemize}[nosep,leftmargin=1em,itemsep=2pt]
  \item[--] We evolved from a basic vector-based RAG to specialized retrieval methods, including SQL for stats and entity lookup, work with real-time sources.
  \item[--] Built cross-domain benchmarks and a quality evaluation framework. Coordinated multiple teams.
\end{itemize}

\noindent\textbf{Voice assistant for messenger}
\hfill \textbf{System Design Architect, LLM Engineer}\par
\begin{itemize}[nosep,leftmargin=1em,itemsep=2pt]
  \item[--] Developed with OpenAI GPT under the hood. Developed an algorithm for spoken contact name recognition, handling variant spellings from different languages.
\end{itemize}

\noindent\textbf{LetAI / Nutrition Estimation Agent}
\hfill \textbf{Solo Lead AI Engineer}\par
\begin{itemize}[nosep,leftmargin=1em,itemsep=2pt]
  \item[--] Developed multimodal LLM-based agent from scratch as a production service: designed strict structured I/O schemas, implemented the full request→LLM→postprocess pipeline (validation, errors, caching), integrated tracing/monitoring, and hardened reliability (rate/length limits, timeouts, error typing).
  \item[--] Built and iterated the evaluation pipeline (benchmarks + automated judging + manual review) to compare model versions and track quality/latency for nutrition extraction.

\end{itemize}

\noindent\textbf{Fashion / AI Stylist}
\hfill \textbf{Solo Lead AI Engineer}\par
\begin{itemize}[nosep,leftmargin=1em,itemsep=2pt]
  \item[--]  Designed and built from scratch an LLM-based AI stylist service that takes outfit requests and generates a complete look (items + combinations) with consistent style, fit, color harmony, weather/temperature, etc.
  \item[--] Built a multimodal LLM garment attribute extractor (style/fit/texture/pattern/color/seasonality) and created the labeled image dataset.
  \item[--] Created a knowledge capture workflow from expert videos (transcription + structured extraction).
\end{itemize}

\footnotesize Technologies: RAG, Routing, SO, CoT, prompt engineering, domain driven design, ElasticSearch, other vector db, FastAPI,
LangChain, Langfuse, LangSmith, RAGAS, Spicy, text2sql, multi-modal agents, Huggingface.\par
\vspace{6pt}


\vspace{6pt}
\noindent\textbf{AI/ML ENGINEER, DATA SCIENTIST | \href{https://www.autodoc.eu/}{AUTODOC EU}}
\hfill \mbox{Oct 2022 -- Mar 2024}\par
\footnotesize EU top \textbf{car-parts e-store} with €1.1B in sales and 5.2M products. Operating in 27 EU countries, 5000+ employees at 8 sites.\par

\noindent\textbf{LLM Analytics Copilot (text-to-SQL \& ad-hoc analytics)}
\hfill \textbf{LLM Engineer / PM}\par
\begin{itemize}[nosep,leftmargin=1em,itemsep=2pt]
  \item[--] Built LLM agents for database co-pilot and ad-hoc analytics using Azure OpenAI and LangChain.
\end{itemize}

\noindent\textbf{Assortment Matching \& Coverage Analytics}
\hfill \textbf{ML Engineer / Data Scientist}\par
\begin{itemize}[nosep,leftmargin=1em,itemsep=2pt]
  \item[--] Clustered car parts by technical fit and customer attributes; built an internal dashboard used by ops teams.
  \item[--] Led data governance and coverage gap assessment; reduced product launch prep time from 2 weeks to 1 day and improved assortment gaps visibility (heatmap), boosting revenue by 8.7\% yearly.
\end{itemize}

\footnotesize Technologies: Azure OpenAI API, LangChain, GloVe, DBSCAN, PCA/TSNE, HuggingFace, GCP, Airflow, SQL, Metabase.\par
\vspace{16pt}


%Experience 2


% ---- WELLNITE (без tabularx) ----
\noindent\textbf{AI/ML ENGINEER | \href{https://wellnite.com}{WELLNITE}}   \hfill{\mbox{Dec 2021 -- Oct 2022}} \par
\footnotesize Well-being \textbf{self-care} and \textbf{medtech} startup hit \$17.6M revenue in 2023 with a 67 person team.\par
\begin{itemize}[nosep,leftmargin=1em,itemsep=3pt]
  \item[--] Built RAG components: data preprocessing, prompt engineering, summarization, and model tuning.
  \item[--] Led product delivery and deployed ML services to production on GCP in collaboration with engineering and support teams.
\end{itemize}
\footnotesize Technologies: Bitbucket, GCP, Flask, NLP, LLMs, GPT OpenAI API, NLTK, HuggingFace, BERT, Converse.\par
\vspace{6pt}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{ML ENGINEER, DATA SCIENTIST | COMMUDATA}    \hfill \hspace{90pt} Feb 2021 - Oct 2021\\[3.75pt]
\footnotesize NLP Startup (England, Portugal, Russia). The idea was - determine an author's psychological state from his texts.\\
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
        \item[--] Developed text anomaly detection model and prototype of Log Anomaly Detection web-app.
        \item[--] Improved the product library with new text-feature extraction, increasing ROC AUC by 7\% .
    \end{itemize}
    \end{minipage}
} \\
\footnotesize Technologies: Streamlit, Linux, SQL, NLTK, Tensorflow, Gensim, Spacy, Autoencoders, LSTM, PCA/TSNE, TS.\\
\end{tabularx}


\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{LEAD CYBERSECURITY ENGINEER | \href{www.pfrf.ru}{PFR in the Komi Republic}}  & \hfill Jun 2011 - Feb 2021 \\
\footnotesize Regional dept. Pension Fund of Russia (160+ employees in regional HQ, 22 district branches)\\
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
        \item[--] Mentoring, hiring, onboarding; IT/business stakeholders collaborating, supervised 22 district depts; Designed RBAC model (10× faster access provisioning) and scaled it across regional offices.
    \end{itemize}
    \end{minipage}
}\\
\footnotesize Technologies: MS SQL, Linux, VPN, Cryptography, bash.\\
\end{tabularx}


%Projects
\section{Projects}

\begin{tabularx}{\linewidth}{ @{}l r@{} }

\textbf{\href{https://abdullin.com/erc/}{Enterprise RAG and Agent Challenge}} & \hfill \textbf{Participant} \\[-2pt]
\multicolumn{2}{@{}X@{}}{
\begin{itemize}[leftmargin=*, nosep]
  \item For \href{https://www.timetoact-group.at/en/insights/the-winner-of-the-enterprise-rag-challenge}{ERC \#2} designed and implemented  \href{https://github.com/Irina-Na/RAG_challenge_v2}{RAG-based agent}, for enterprise information retrieval tasks.
  \item  For \href{https://erc.timetoact-group.at/}{ERC \#3} designed and implemented  \href{https://github.com/Irina-Na/SGR_agent_for_ERC3}{agents with different architectures}.
\end{itemize}
} \\[-8pt]

\textbf{\href{https://play.google.com/store/apps/datasafety?id=ru.exhibition.prod}{DariaAI}} & \hfill \textbf{As Sr.ML engineer} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
Navigation chatbot for one of the top exhibition spaces globally (30M+ yearly visitors) website and mobile app (200K+ users).
Implemented entity extraction, optimized search engine, and developed search logging and data prep service (annotation, summarizing) using LLMs, enhancing chatbot performance and UX.
} \\ [30pt]

\textbf{\href{https://www.youtube.com/@CreativeWorkshop-s}{CreativeWorkshops} -- AI Research \& Community Initiative} & \hfill \textbf{Co-organizer} \\[-8pt]
\multicolumn{2}{@{}X@{}}{
\begin{itemize}[leftmargin=*, nosep]
  \item Active member of \href{https://t.me/ods_ns/2504}{the local} division of \href{https://old.ods.ai/en/}{OpenDataScience} community and co-organizer of  \href{https://t.me/+AK0U2AOuqgFjYWJi}{AI research community}.
  \item Co-organized meetups and public talks on applied AI; created a platform for local experts across diverse fields to share knowledge. Maintainer of the community \href{https://www.youtube.com/@CreativeWorkshop-s}{YouTube channel}.
\end{itemize}
} \\[-8pt]

\end{tabularx}


%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}
% --- Associate Professor (Adjunct) ---
\multicolumn{2}{@{}X@{}}{
  \begin{tabularx}{\linewidth}{@{}X r@{}}
    \textbf{Associate Professor (Adjunct) at \href{https://en.syktsu.ru/}{Syktyvkar State University}}
     \textit{\mbox{remote}}
  \end{tabularx}
} \\
\multicolumn{2}{@{}X@{}}{
\footnotesize
Taught neural networks and applied AI for future cybersecurity specialists.
} \\[4pt]

2011 - 2016 & PhD (Modeling and Security) at \textbf{\href{http://www.spiiras.nw.ru/en/}{St. Petersburg Institute for Informatics and Automation Russian Academy of Sciences (SPIIRAS)}} \\

2005 - 2010 & Masters Degree (with Honors) at \textbf{\href{https://en.syktsu.ru/}{Syktyvkar State University}} ranked top1 in the Komi Republic, Information security specialist \\[-4pt]

\end{tabularx}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------
\section{Publications}
\footnotesize
\begin{refsection}[citations.bib]
\nocite{nosal2011modeling, nosal2013justification}
\printbibliography[heading=none]
\end{refsection}
\endgroup
%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}

{\footnotesize
\setlength{\tabcolsep}{1pt}
\renewcommand{\arraystretch}{1.0}
\begin{tabularx}{\linewidth}{@{}l X@{}}
LLM and NLP & Transformers, prompt engineering, fine-tuning, CoT, SGR, SO, LangSmith, Langfuse, BM25, FAISS, Hugging Face, BERT, Spacy, Gensim, Glove, NLTK, .\\
ML & DL, Tensorflow, PyTorch, Prophet, Catboost, Autoencoders, LSTM, PCA, TSNE, Matching, Clustering, Anomaly detection, Time Series, Visualization.\\
Data & SQL (PostgreSQL, Clickhouse, MS SQL, MySQL), Metabase, BigQuery, Airflow.\\
Development & FastAPI, Flask, Streamlit, Sentry, deploying on GCP, Bitbucket, GitLab and GitHub ci-cd.\\
Base & Python, Git, Docker, Linux, bash, Jira.\\
\end{tabularx}
}


\vfill
\center{\footnotesize Last updated: \today}
\end{document}
